---
title: "Final project"
author: "Group4"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(infer)
library(dplyr)
library(ggplot2)
```



```{r}
fashion <- readxl::read_excel("fashion_data_2018_2022.xls")
```

# Numerical Variables

## price - ChaeJun Lim
### Histogram
```{r}
fashion %>%
  ggplot()+
  geom_histogram(mapping = aes(x=price), binwidth=30, color="black",
                 fill="skyblue")+
  labs(
  title = "Price Histogram",
  x = "Price",
  y = "Count"
  )
```

### Scatterplot
```{r}
fashion %>%
  ggplot()+
  geom_point(mapping = aes(x=price, y=sales_count))+
  labs(
  title = "Price and Sales Count Scatterplot",
  x = "Price",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(price, sales_count, FUN=median)))+
  labs(
  title = "Price and Sales Count Boxplot",
  x = "Price",
  y = "Sales Count"
  )
```

## reviews_count - ChaeJun Lim

### Histogram

```{r}
fashion %>%
  ggplot()+
  geom_histogram(mapping = aes(x=reviews_count), binwidth=20, 
                 color = "black", fill = "skyblue")+
  labs(
  title = "Reviews Count Histogram",
  x = "Reviews Count",
  y = "Count"
  )
```

### Scatterplot

```{r}
fashion %>%
  ggplot()+
  geom_point(mapping = aes(x=reviews_count, y=sales_count))+
  labs(
  title = "Reviews Count and Sales Count Scatterplot",
  x = "Reviews Count",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(reviews_count, sales_count,
                                          FUN=median)))+
  labs(
  title = "Reviews Count and Sales Count Boxplot",
  x = "Reviews Count",
  y = "Sales Count"
  ) +
  theme(axis.text.x = element_text(angle = 45))
```

## wish_list_count - Jin Heo

### Histogram
```{r}
fashion %>%
  ggplot()+
  geom_histogram(mapping = aes(x=wish_list_count), binwidth=50, 
                 color="black", fill="skyblue")+
  labs(
  title = "Wish List Count Histogram",
  x = "Wish List Count",
  y = "Count"
  )
```

### Scatterplot
```{r}
fashion %>%
  ggplot()+
  geom_point(mapping = aes(x=wish_list_count, y=sales_count))+
  labs(
  title = "Wish List Count and Sales Count Scatterplot",
  x = "Wish List Count",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(wish_list_count, sales_count,
                                            FUN=median)))+
  labs(
  title = "Wish List Count and Sales Count Boxplot",
  x = "Wish List Count",
  y = "Sales Count"
  ) +
  theme(axis.text.x = element_text(angle = 45))
```

# Categorical Variables Visualization

## gender - Jin Heo

### Bar graph

```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= gender), binwidth=30)+
  labs(
  title = "Gender and Sales Count Bar Graph",
  x = "Gender",
  y = "Sales Count"
  )
```

```{r, fig.width=14}
fashion %>%
  ggplot()+
  geom_histogram(mapping = aes(x= sales_count), binwidth=70, color = "black",
                 fill = "grey") + facet_wrap(~ gender) +
  labs(
  title = "Gender Histogram",
  x = "Gender",
  y = "Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(gender, sales_count, FUN=median)))+
  labs(
  title = "Gender and Sales Count Boxplot",
  x = "Gender",
  y = "Sales Count"
  )
```

## category - Minseo Yoon

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= category), binwidth=30)+
  labs(
  title = "Category and Sales Count Bar Graph",
  x = "Category",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(category, sales_count,
                                            FUN=median)))+
  labs(
  title = "Category and Sales Count Boxplot",
  x = "Category",
  y = "Sales Count"
  )
```

## pattern - Minseo Yoon

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= pattern), binwidth=30)+
  labs(
  title = "Pattern and Sales Count Bar Graph",
  x = "Pattern",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(pattern, sales_count,
                                            FUN=median)))+
  labs(
  title = "Pattern and Sales Count Boxplot",
  x = "Pattern",
  y = "Sales Count"
  )
```

## color - Seunghyun Ryu

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= color), binwidth=30)+
  labs(
  title = "Color and Sales Count Bar Graph",
  x = "Color",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(color, sales_count,
                                            FUN=median)))+
  labs(
  title = "Color and Sales Count Boxplot",
  x = "Color",
  y = "Sales Count"
  )
```

## age group - Seunghyun Ryu

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= age_group), binwidth=30)+
  labs(
  title = "Age Group and Sales Count Bar Graph",
  x = "Age Group",
  y = "Sales Count"
  )
```

### Histogram

```{r, fig.width=14}
fashion %>%
  ggplot()+
  geom_histogram(mapping = aes(x= sales_count), binwidth=70, color = "black",
                 fill = "grey") + facet_wrap(~ age_group) +
  labs(
  title = "Age Group Histogram",
  x = "Age Group",
  y = "Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x= reorder(age_group, sales_count,
                                             FUN=median)))+
  labs(
  title = "Age Group and Sales Count Boxplot",
  x = "Age Group",
  y = "Sales Count"
  )
```

## season - Juheon Kim

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= season), binwidth=30)+
  labs(
  title = "Season and Sales Count Bar Graph",
  x = "Season",
  y = "Sales Count"
  )
```

### Histogram

```{r, fig.width=14}
fashion %>%
  ggplot()+
  geom_histogram(mapping = aes(x= sales_count), binwidth=70, color = "black",
                 fill = "grey") + facet_wrap(~ season) +
  labs(
  title = "Season Histogram",
  x = "Season",
  y = "Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(season, sales_count,
                                            FUN=median)))+
  labs(
  title = "Season and Sales Count Boxplot",
  x = "Season",
  y = "Sales Count"
  )
```

## material - Juheon Kim

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= material), binwidth=30)+
  labs(
  title = "Material and Sales Count Bar Graph",
  x = "Material",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(material, sales_count,
                                            FUN=median)))+
  labs(
  title = "Material and Sales Count Boxplot",
  x = "Material",
  y = "Sales Count"
  )
```

## average rating - Hyukjoon Choi

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= average_rating), binwidth=30)+
  labs(
  title = "Average Rating and Sales Count Bar Graph",
  x = "Average Rating",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(average_rating, sales_count,
                                            FUN=median)))+
  labs(
  title = "Average Rating and Sales Count Boxplot",
  x = "Average Rating",
  y = "Sales Count"
  )
```

## discount - Hyukjoon Choi

### Bar graph
```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x= discount), binwidth=30)+
  labs(
  title = "Discount and Sales Count Bar Graph",
  x = "Discount",
  y = "Sales Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(discount, sales_count,
                                            FUN=median)))+
  labs(
  title = "Discount and Sales Count Boxplot",
  x = "Discount",
  y = "Sales Count"
  )
```

## out_of_stock_times - ChaeJun Lim

### Histogram

```{r}
fashion %>%
  ggplot()+
  geom_bar(mapping = aes(x=out_of_stock_times), binwidth=30)+
  labs(
  title = "Out of Stock Times and Sales Count Bar Graph",
  x = "Out of Stock Times",
  y = "Count"
  )
```

### Boxplot
```{r}
fashion %>%
  ggplot()+
  geom_boxplot(aes(y=sales_count, x=reorder(out_of_stock_times,
                                            sales_count, FUN=median)))+
  labs(
  title = "Out of Stock Times and Sales Count Boxplot",
  x = "Out of Stock Times",
  y = "Sales Count"
  )
```

# Hypothesis 1

## Gender & Sales Count - ChaeJun Lim, Hyukjoon Choi

### Hypothesis: There is at least one relationship between gender and sales count.
### Alternative: There is at least relationship between gender and sales count.

### Male & Female

```{r}
fashion %>%
  select(sales_count) %>%
  arrange(desc(sales_count)) %>%
  head(5)
```
```{r}
fashion %>%
  select(sales_count) %>%
  arrange(sales_count) %>%
  head(5)
```


```{r}
fashion %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = gender),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of gender",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion %>%
  group_by(gender) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```
```{r}
fashion_gender_null <- fashion %>%
  specify(formula = sales_count ~ gender) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Male", "Female"))
```

```{r}
fashion_gender_obs_stat <- fashion %>%
  specify(sales_count ~ gender) %>%
  calculate(stat = "diff in means", order = c("Male", "Female"))
```

```{r}
fashion_gender_null %>%
  get_p_value(obs_stat = fashion_gender_obs_stat, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_gender_null) +
  shade_p_value(obs_stat = fashion_gender_obs_stat, direction = "two_sided") +
  labs(
  title = "Simulation (gender)",
  x = "difference in proportions",
  y = "count"
  )
```

# Hypothesis 2

## Age & Sales Count - Seunghyun Ryu, Miseo Yoon

### Hypothesis: There is a relationship between age and sales count.
### Alternative: There is no relationship between age and sales count.

### 18-24 & 25-35

```{r}
fashion_age <- fashion %>%
  filter(age_group == "18-24" | age_group == "25-35")
```

```{r}
fashion_age %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = age_group),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of age group (18-24 & 25-35)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_age %>%
  group_by(age_group) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```
```{r}
fashion_age_null <- fashion_age %>%
  specify(formula = sales_count ~ age_group) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("18-24", "25-35"))
```

```{r}
fashion_age_obs_stat <- fashion_age %>%
  specify(sales_count ~ age_group) %>%
  calculate(stat = "diff in means", order = c("18-24", "25-35"))
```

```{r}
fashion_age_null %>%
  get_p_value(obs_stat = fashion_age_obs_stat, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_age_null) +
  shade_p_value(obs_stat = fashion_age_obs_stat, direction = "two_sided") +
  labs(
  title = "Simulation 1 (18-24 & 25-35)",
  x = "difference in proportions",
  y = "count"
  )
```

### 18-24 & 35-45

```{r}
fashion_age_2 <- fashion %>%
  filter(age_group == "18-24" | age_group == "35-45")
```

```{r}
fashion_age_2 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = age_group),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of age group (18-24 & 35-45)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_age_2 %>%
  group_by(age_group) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```
```{r}
fashion_age_null_2 <- fashion_age_2 %>%
  specify(formula = sales_count ~ age_group) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("18-24", "35-45"))
```

```{r}
fashion_age_obs_stat_2 <- fashion_age_2 %>%
  specify(sales_count ~ age_group) %>%
  calculate(stat = "diff in means", order = c("18-24", "35-45"))
```

```{r}
fashion_age_null_2 %>%
  get_p_value(obs_stat = fashion_age_obs_stat_2, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_age_null_2) +
  shade_p_value(obs_stat = fashion_age_obs_stat_2, direction = "two_sided") +
  labs(
  title = "Simulation 2 (18-24 & 35-45)",
  x = "difference in proportions",
  y = "count"
  )
```

### 25-35 & 35-45

```{r}
fashion_age_3 <- fashion %>%
  filter(age_group == "25-35" | age_group == "35-45")
```

```{r}
fashion_age_3 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = age_group),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of age group (25-35 & 35-45)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_age_3 %>%
  group_by(age_group) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```
```{r}
fashion_age_null_3 <- fashion_age_3 %>%
  specify(formula = sales_count ~ age_group) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("25-35", "35-45"))
```

```{r}
fashion_age_obs_stat_3 <- fashion_age_3 %>%
  specify(sales_count ~ age_group) %>%
  calculate(stat = "diff in means", order = c("25-35", "35-45"))
```

```{r}
fashion_age_null_3 %>%
  get_p_value(obs_stat = fashion_age_obs_stat_3, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_age_null_3) +
  shade_p_value(obs_stat = fashion_age_obs_stat_3, direction = "two_sided") +
  labs(
  title = "Simulation 3 (25-35 & 35-45)",
  x = "difference in proportions",
  y = "count"
  )
```


# Hypothesis 3

## Season & Sales Count - Jin Heo, Juheon Kim

### Hypothesis: There is at least one relationship between age and sales count.
### Alternative: There is at least relationship between age and sales count.

### All & Spring

```{r}
fashion_season <-fashion %>%
  filter(season == "All" | season == "Spring")
```

```{r}
fashion_season %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (All & Spring)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_season %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null <- fashion_season %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("All", "Spring"))
```

```{r}
fashion_season_obs_stat <- fashion_season %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("All", "Spring"))
```

```{r}
fashion_season_null %>%
  get_p_value(obs_stat = fashion_season_obs_stat, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null) +
  shade_p_value(obs_stat = fashion_season_obs_stat, direction = "two_sided") +
  labs(
  title = "Simulation 1 (All & Spring)",
  x = "difference in proportions",
  y = "count"
  )
```

### All & Summer

```{r}
fashion_season_2 <-fashion %>%
  filter(season == "All" | season == "Summer")
```

```{r}
fashion_season_2 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (All & Summer)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_season_2 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_2 <- fashion_season_2 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("All", "Summer"))
```

```{r}
fashion_season_obs_stat_2 <- fashion_season_2 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("All", "Summer"))
```

```{r}
fashion_season_null_2 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_2, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_2) +
  shade_p_value(obs_stat = fashion_season_obs_stat_2, direction = "two_sided") +
  labs(
  title = "Simulation 2 (All & Summer)",
  x = "difference in proportions",
  y = "count"
  )
```

### All & Autumn

```{r}
fashion_season_3 <-fashion %>%
  filter(season == "All" | season == "Autumn")
```

```{r}
fashion_season_3 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (All & Autumn)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_season_3 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_3 <- fashion_season_3 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("All", "Autumn"))
```

```{r}
fashion_season_obs_stat_3 <- fashion_season_3 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("All", "Autumn"))
```

```{r}
fashion_season_null_3 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_3, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_3) +
  shade_p_value(obs_stat = fashion_season_obs_stat_3, direction = "two_sided") +
  labs(
  title = "Simulation 3 (All & Autumn)",
  x = "difference in proportions",
  y = "count"
  )
```

### All & Winter

```{r}
fashion_season_4 <-fashion %>%
  filter(season == "All" | season == "Winter")
```

```{r}
fashion_season_4 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (All & Winter)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_season_4 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_4 <- fashion_season_4 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("All", "Winter"))
```

```{r}
fashion_season_obs_stat_4 <- fashion_season_4 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("All", "Winter"))
```

```{r}
fashion_season_null_4 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_4, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_4) +
  shade_p_value(obs_stat = fashion_season_obs_stat_4, direction = "two_sided") +
  labs(
  title = "Simulation 4 (All & Winter)",
  x = "difference in proportions",
  y = "count"
  )
```

### Spring & Summer

```{r}
fashion_season_5 <-fashion %>%
  filter(season == "Spring" | season == "Summer")
```

```{r}
fashion_season_5 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (Spring & Summer)",
  x = "Sales Count",
  y = "Count"
  )
```

```{r}
fashion_season_5 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_5 <- fashion_season_5 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Spring", "Summer"))
```

```{r}
fashion_season_obs_stat_5 <- fashion_season_5 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("Spring", "Summer"))
```

```{r}
fashion_season_null_5 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_5, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_5) +
  shade_p_value(obs_stat = fashion_season_obs_stat_5, direction = "two_sided") +
  labs(
  title = "Simulation 5 (Spring & Summer)",
  x = "difference in proportions",
  y = "count"
  )
```


### Spring & Autumn

```{r}
fashion_season_6 <- fashion %>%
  filter(season == "Spring" | season == "Autumn")
```

```{r}
fashion_season_6 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (Spring & Autumn)",
  x = "Sales Count",
  y = "Count"
  )
```


```{r}
fashion_season_6 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_6 <- fashion_season_6 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Spring", "Autumn"))
```

```{r}
fashion_season_obs_stat_6 <- fashion_season_6 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("Spring", "Autumn"))
```

```{r}
fashion_season_null_6 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_6, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_6) +
  shade_p_value(obs_stat = fashion_season_obs_stat_6,
                direction = "two_sided") +
  labs(
  title = "Simulation 6 (Spring & Autumn)",
  x = "difference in proportions",
  y = "count"
  )
```

### Spring & Winter
```{r}
fashion_season_7 <- fashion %>%
  filter(season == "Spring" | season == "Winter")
```


```{r}
fashion_season_7 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (Spring & Winter)",
  x = "Sales Count",
  y = "Count"
  )
```


```{r}
fashion_season_7 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_7 <- fashion_season_7 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Spring", "Winter"))
```

```{r}
fashion_season_obs_stat_7 <- fashion_season_7 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("Spring", "Winter"))
```

```{r}
fashion_season_null_7 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_7, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_7) +
  shade_p_value(obs_stat = fashion_season_obs_stat_7, direction = "two_sided") +
  labs(
  title = "Simulation 7 (Spring & Winter)",
  x = "difference in proportions",
  y = "count"
  )
```

### Summer & Autumn

```{r}
fashion_season_8 <- fashion %>%
  filter(season == "Summer" | season == "Autumn")
```


```{r}
fashion_season_8 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (Summer & Autumn)",
  x = "Sales Count",
  y = "Count"
  )
```


```{r}
fashion_season_8 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_8 <- fashion_season_8 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Summer", "Autumn"))
```

```{r}
fashion_season_obs_stat_8 <- fashion_season_8 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("Summer", "Autumn"))
```

```{r}
fashion_season_null_8 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_8, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_8) +
  shade_p_value(obs_stat = fashion_season_obs_stat_8, direction = "two_sided") +
  labs(
  title = "Simulation 8 (Summer & Autumn)",
  x = "difference in proportions",
  y = "count"
  )
```

### Summer & Winter

```{r}
fashion_season_9 <- fashion %>%
  filter(season == "Summer" | season == "Winter")
```

```{r}
fashion_season_9 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (Summer & Winter)",
  x = "Sales Count",
  y = "Count"
  )
```


```{r}
fashion_season_9 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_9 <- fashion_season_9 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Summer", "Winter"))
```

```{r}
fashion_season_obs_stat_9 <- fashion_season_9 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("Summer", "Winter"))
```

```{r}
fashion_season_null_9 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_9, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_9) +
  shade_p_value(obs_stat = fashion_season_obs_stat_9, direction = "two_sided") +
  labs(
  title = "Simulation 9 (Summer & Winter)",
  x = "difference in proportions",
  y = "count"
  )
```

### Autumn & Winter

```{r}
fashion_season_10 <- fashion %>%
  filter(season == "Autumn" | season == "Winter")
```

```{r}
fashion_season_10 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = sales_count, fill = season),
  binwidth = 15, alpha = 0.3, position = "identity") +
  coord_cartesian(xlim = c(50,500)) +
  labs(
  title = "histogram of season (Autumn & Winter)",
  x = "Sales Count",
  y = "Count"
  )
```


```{r}
fashion_season_10 %>%
  group_by(season) %>%
  summarize(
    mean = mean(sales_count),
    median = median(sales_count),
    sd = sd(sales_count),
    min = min(sales_count),
    max = max(sales_count),
    IQR = IQR(sales_count)
  )
```

```{r}
fashion_season_null_10 <- fashion_season_10 %>%
  specify(formula = sales_count ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Autumn", "Winter"))
```

```{r}
fashion_season_obs_stat_10 <- fashion_season_10 %>%
  specify(sales_count ~ season) %>%
  calculate(stat = "diff in means", order = c("Autumn", "Winter"))
```

```{r}
fashion_season_null_10 %>%
  get_p_value(obs_stat = fashion_season_obs_stat_10, direction = "two_sided")
```

```{r, warning=FALSE}
visualize(fashion_season_null_10) +
  shade_p_value(obs_stat = fashion_season_obs_stat_10, direction = "two_sided") +
  labs(
  title = "Simulation 10 (Autumn & Winter)",
  x = "difference in proportions",
  y = "count"
  )
```


